Rewind: Automatically Generated\\Digital Memories from Mobile Geolocation Data

### 2016-09-14 paper/uist_2016/paper.tex
added one flowchart; changed abstract

\begin{abstract}
The Rewind system automatically recreates a digital memory of a past trip. It takes historical geolocation data and generates a stitched-together video made of streetside images from where a user has been. The images are manipulated based on the weather, time of day, and season to look like what the user may have seen when they were there. Users can go back and forth in time by scrubbing their pointer left or right over the video. Together, the composed Rewinds offer users a window into past travels. A user study of people collecting location data over two weeks reveals that users can remember the location from a photograph about half of the time, but when shown a Rewind, they can nearly always remember where they traveled. Furthermore, GPS users are less likely to remember the specifics of a location, and people are particularly interested in preserving Rewinds of infrequent trips and trips taken with others. Rewind serves as an experiment of the extreme scenario where people can freely roam and experience the world, keeping their mobile devices in their pockets, and still generate believable representations that capture the past.
\end{abstract}

@@

\section{The Rewind System}
\textit{Rewind} recreats the visual sensation of travelling down past routes using raw Google Location History data retrieved by lifeloggers. Differing from previously studied hyperlapse creation techniques by Kopft et al. and Joshi et al \cite{opf:2014:FHV:2601097.2601195, Joshi:2015:RHC:2809654.2766954}, \textit{Rewind} does not require any cinematic archives from the users, and it is computationally lightweight. \textit{Rewind} inputs lifeloggers' geolocation data, maps out tracked trajectories, and outputs photo-video pairs with Google Street View images. The sceneries in each photo-video pair are customized for each user based on times of the day, meteorological conditions and seasonal changes when the route was taken, providing users with multi-dimensional temporal cues. \textit{Rewind} is a client-side only application implemented with Google Maps API and third-party JavaScript libraries, and therefore does not transfer sensitive user data nor store it.

>>>>

\begin{abstract}
GPS tracking using smartphones have been prevalent, providing self-trackers insights into their past visits and traveling patterns. Using tracked GPS information, we proposed \textit{Rewind}, a system that recreates sceneries of past trips to assist the recall of episodic memory. \textit{Rewind} takes historical GPS data from the users, maps out movement trajectories, and generates stitched-together videos to simulate the ways how past trips were taken. Users of \textit{Rewind} can change their moving directions by scrubbing their pointers over the video. Images used in \textit{Rewind} videos are post-processed to reveal weather and timely characteristics of the emulated environment.  Our study of self-trackers using two-week of GPS data with \textit{Rewind} has revealed that non-GPS users tend to think \textit{Rewind} videos have accurately captured their past trips, and users are particularly interested in preserving \textit{Rewind} videos of infrequent trips and trips accompanied by others. Overall, \textit{Rewind} serves as an experiment of the extreme scenario where people can freely roam and experience the world, keeping their mobile devices in their pockets, and still generate believable representations that capture the past.
\end{abstract}

@@

\section{The Rewind System}
\textit{Rewind} recreats the visual sensation of travelling down past routes using raw Google Location History data retrieved by lifeloggers. Differing from previously studied hyperlapse creation techniques by Kopft et al. and Joshi et al \cite{opf:2014:FHV:2601097.2601195, Joshi:2015:RHC:2809654.2766954}, \textit{Rewind} does not require any cinematic archives from the users, and it is computationally lightweight. \textit{Rewind} inputs lifeloggers' geolocation data, maps out tracked trajectories, and outputs photo-video pairs with Google Street View images. The sceneries in each photo-video pair are customized for each user based on times of the day, meteorological conditions and seasonal changes when the route was taken, providing users with multi-dimensional temporal cues. \textit{Rewind} is a client-side only application implemented with Google Maps API and third-party JavaScript libraries, and therefore does not transfer sensitive user data nor store it. \ref{fig:flowchart}

\begin{figure}
     \includegraphics[width=1\linewidth]{Rewind-flowchart}
     \caption{Plantation is classified using HSV color space, and the HSV values were adjusted to reflect seasonal changes}
     \label{fig:flowchart}
\end{figure}
